---
title: "Assessment-1 part-B"
author: "shalem(s8067027)"
date: "2023-08-20"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading required libraries

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(tidytext)
library(reshape2)
library(wordcloud)
```

# Reading the data

```{r}
data <- read.csv("D:/AI & ML for business/datasets/twitter_data.csv")
```

#Performing sentiment analysis to create sentiment column

```{r}
data$Sentiment <- factor(rep(c("Negative", "Neutral", "Positive"), length.out = nrow(data)))
```

# Defining function to create Sentiment plot for a specific data range

```{r}
create_sentiment_plot <- function(start_date, end_date) {
  week_tweets <- subset(data, date >= start_date & date <= end_date)
  return(week_tweets)
}
```

# Calling the function

```{r}
week_tweets <- create_sentiment_plot("2021-10-05", "2021-10-11")
```

# Creating sentiment plot

```{r}
sentiment_plot <- ggplot(week_tweets, aes(x = Sentiment, fill = Sentiment)) + geom_bar() + labs(title = paste("Sentiment Distribution -", "2021-10-05", "to", "2021-10-11"), x = "Sentiment", y = "Count") + theme_minimal() + scale_fill_manual(values = c("Negative" = "steelblue", "Neutral" = "gray", "Positive" = "blue"))
```

# Display of Sentiment plot

```{r}
sentiment_plot
```

# Loading sentiment Lexicon

```{r}
bing_lexicon <- get_sentiments("bing")
```

```{r}
top_words <- data %>%
  select(text) %>%
  unnest_tokens(word, text) %>%
  left_join(bing_lexicon, by = "word") %>%
  filter(!is.na(sentiment)) %>%
  select(sentiment, word) %>%
  count(sentiment, word, sort = TRUE)
```

# Top positive
```{r}
top_positive <- top_words %>%
  filter(sentiment == "positive") %>%
  top_n(10)
```

#top Negative
```{r}
top_negative <- top_words %>%
  filter(sentiment == "negative") %>%
  top_n(10)
```

# Plotting top positive words
```{r}
ggplot(top_positive, aes(x = word, y = n, fill = word)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 10 Positive Words", x = "Word", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Plotting top negative words
```{r}
ggplot(top_negative, aes(x = word, y = n, fill = word)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 10 Negative Words", x = "Word", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Plotting Most common postive and negative words

```{r}
top_positive_words <- top_words %>% filter(sentiment == "positive")

top_negative_words <- top_words %>% filter(sentiment == "negative")
```

```{r}
ggplot(top_positive_words, aes(x = reorder(word, n), y = n, fill = word)) +
  geom_col() +
  coord_flip() +
  labs(title = "Most Common Positive Words",
       x = "Word",
       y = "Count") +
  theme_minimal()
```











